Group Signatures Meet Anonymous Credentials: Or, How to Build Privacy Preserving Identities with Accountability

### 2022-02-22 prism-backend/research/gsac/uas-model.tex
Security of fiss, feval and finsp was ignored. Should go on trace.

\todo{Domains (attributes, messages, etc.) are not correctly defined here. But
  for now, just leave it as is to at least convey the idea. Also, this needs
  refinement in general: what properties (if any) do these functions need to
  meet in order to be meaningful?}
\begin{description}
\item[$\fissue: (\uattrs,\dattrs) \rightarrow 0/1$.] Governs what customized
  conditions an issuer requires in order to issue credentials, when receiving
  a request from a user with a set of disclosed attributes \dattrs, and
  undisclosed attributes \uattrs (which need to be kept private from the
  issuer). \fissue returns 1 to accept a request, 0 to reject it.  
\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Governs customized
  conditions to define whether the owner of a user key and set of credentials --
  or, more specifically, credentials encoding certain attributes -- should be
  able to sign certain messages.
\item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
  utility value, derived from the user's public key, credentials, signed
  message, and produced signature (or a subset thereof), should be extractable
  by the group inspector.
\end{description}

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new inspector to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
  which credential was used to produce it.
\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
  set of attributes, and a message, returns a signature produced by one of these
  two credentials, defined by the bit $b$, which is established in the anonymity
  game.
\end{description}

@@

        \procedure{$\CHALb(\msg,
          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},
          \tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%          
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
          \pcif \feval(\msg,\CRED[\scid_0]) \neq \feval(\msg,\CRED[\scid_1]):
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\cscid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

\begin{figure}[htp!]
  \procedure{$\ExpTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\sig,\dattrs,\msg) \gets
     \adv^{\Otrace}(\parm) \\
     \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~( \\
     \pcind \pccomment{All \Obtain transcripts fail to open \sig} \\
     \pcind \nexists \gid \in \sgid:
     \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) = \bot~\lor \\
     \pcind \pccomment{Such transcript exists, but ...} \\
     \pcind \exists\gid \in \sgid~\st~
     \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs) =
     (\y,\iproof)~\land (\\
     \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
     \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 0~\lor \\
     \pcind \pcind \pccomment{... or \Judge accepts the proof, but inspect
       returns an invalid value} \\
     \pcind \pcind \nexists \uid \in \CU \cup \HU~\st~
     \y = \finsp(\PUBUK[\uid],\CRED[\uid],\sig) \\
     \pcind ) \\
     ) \\
     \pcreturn 0
  }
  \caption{Traceability experiment for \UAS schemes.}
  \label{fig:exp-uas-trace}
\end{figure}

>>>>

\begin{description}
\item[$\fissue: (\uattrs,\dattrs) \rightarrow 0/1$.] Governs what customized
  conditions an issuer requires in order to issue credentials, when receiving
  a request from a user with a set of disclosed attributes \dattrs, and
  undisclosed attributes \uattrs (which need to be kept private from the
  issuer). \fissue returns 1 to accept a request, 0 to reject it.  
\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Governs customized
  conditions to define whether the owner of a user key and set of credentials --
  or, more specifically, credentials encoding certain attributes -- should be
  able to sign certain messages.
\item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
  utility value, derived from the user's public key, credentials, signed
  message, and produced signature (or a subset thereof), should be extractable
  by the group inspector.
\end{description}

\todo{\fissue and \feval are not covered in the security definitions! Probably,
  they should go into traceability -- which may need to be generalized into
  unforgeability or something like that.}

\paragraph{Helper Function \Identify.} In addition, we make use of a helper
function \Identify for our non-frameability definition. This function receives
a signature and a user secret key, and determines whether the latter was used
to produce the former. This is in line with previous works on DAA
\cite{bfg+11,cdl16} and group signatures without traditional open functions
\cite{dl21,fgl21,gl19}. More concreltely \Identify function, defined as $1/0
\gets \Identify(\usk,\sig)$, conveys meaning to our non-frameability definition
conditioned on the fact that, given a signature \sig accepted by \Verify,
\Identify returns $1$ for exactly one \usk.

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new inspector to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
  key to the adversary.
\item[\OCORR.] Corrupts an existing (and honest) inspector, by giving its secret
  key to the adversary.  
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
  which credential was used to produce it.
\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
  set of attributes, and a message, returns a signature produced by one of these
  two credentials, defined by the bit $b$, which is established in the anonymity
  game.
\end{description}

@@

        \procedure{$\CHALb(\msg,
          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},
          \tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%          
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
          \pcif \feval(\PUBUK[\uid_0],\CRED[\scid_0],\msg) \neq \\
          \pcind \feval(\PUBUK[\uid_1],\CRED[\scid_1],\msg):
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\cscid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

\begin{figure}[htp!]
%  \begin{minipage}[t]{\textwidth}
    \procedure{$\ExpTrace(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\sig,\dattrs,\msg,\sgid) \gets
      \adv^{\Otrace}(\parm) \\
      \pcreturn 1~\pcif: \\
      \pcind \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~(
      \IssueForge(\sig,\msg,\dattrs,\sgid) = 1~\lor \\
      \pcind \pcind \EvalForge(\sig,\msg,\dattrs,\sgid) = 1~\lor~
      \InspectForge(\sig,\msg,\dattrs,\sgid) = 1) \\
      \pcreturn 0 \\
    }

  % \end{minipage}
  % \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\IssueForge(\sig,\msg,\dattrs,\sgid)$}{%
      \pcreturn 0 \\
    }

    \procedure{$\EvalForge(\sig,\msg,\dattrs,\sgid)$}{%
      \feval(\PUBUK[\uid],\CRED[\uid],\msg) = 0 \\
      \pcreturn 0 \\
    }

    \procedure{$\InspectForge(\sig,\msg,\dattrs,\sgid)$}{%
      \pcreturn 1~\pcif: \\
      \pcind \pccomment{All \Obtain transcripts fail to inspect \sig} \\
      \pcind \nexists \gid \in \sgid:
      \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) = \bot~\lor \\
      \pcind \pccomment{A valid transcript exists, but ...} \\
      \pcind \exists\gid \in \sgid~\st~
      \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs) =
      (\y,\iproof)~\land (\\
      \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
      \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 0~\lor \\
      \pcind \pcind \pccomment{... or \Judge accepts the proof, but \Inspect
      returns an invalid value \y} \\
      \pcind \pcind \nexists \uid \in \CU \cup \HU~\st~
      \y = \finsp(\PUBUK[\uid],\CRED[\uid],\sig) \\
      \pcind ) \\      
      \pcreturn 0
    }
%  \end{minipage}      
  \caption{Traceability experiment for \UAS schemes.}
  \label{fig:exp-uas-trace}
\end{figure}
